### 2023-08-10 chapters/acknowledgements.tex
acknowledgement

I feel incredibly fortunate to have had the opportunity to collaborate with exceptional individuals throughout my research journey. Debabrota Basu, Dmitry Malioutov, Krisnha P. Gummadi, Daniel Neider, Arijit Khan, Jonathan Scarlet, Chandrika Bhardwaj, Vijay Saraswat, Naheed Anjum Arafat, and Lorenzo Ciampiconi are among the remarkable collaborators who have generously shared their knowledge and experience with me. I come to understand that finding a meaningful research problem is a crucial step and I am grateful to have had the opportunity to collaborate and brainstorm with such insightful collaborators.

I would like to express my sincere appreciation to my friends in Singapore who have provided invaluable support throughout my journey. Neamul Kabir, Sanjay Saha, Amlan Saha, Rafiul Islam, Zubair Faruqui, Mohimenul Mahi, Ramzan Miah, Muhim Muktadir Zim, and Shayok Ghosh have been pillars of support and encouragement. I am also grateful for the exceptional colleagues who have made a significant impact on my professional growth. Priyanka Golia, Teodora Baluta, Yash Pote, Arijit Shaw, Suwei Yang, Jiong Yang, Mate Soos, Tim van Bremen, Anna Latour, Yacine Izza, Gunjan Kumar, Paulius Dilkas, Shubham Sharma, Rahul Gupta, and Zhanzhong Pang have been sources of inspiration and collaboration. I truly believe that it takes an entire village to achieve something incredible, and I am fortunate to have such a supportive community. Additionally, I extend my thanks to all the staff members in SOC, NUS for their exceptional efficiency in addressing students' needs.

I would like to express my heartfelt gratitude to my family for their support and encouragement. My parents, sister, brother-in-law, and uncle have been constant pillars of strength throughout my journey. While I deeply regret that my father is not here with me today, I find solace in the belief that his blessings will always guide me. I am also immensely grateful to my wife, Dola Ghosh, who has been my unwavering source of support and companionship throughout this challenging journey. Her presence has made the road to completion much smoother, and I am grateful for her love and encouragement. Additionally, I would like to extend a special thank you to my childhood friends, Kalyan Roy, Sukanto Kundu, Nayem Ul Haque, and Niranjan Chandra Roy. Their friendship has been a constant source of strength and support throughout my life.

>>>>

I feel incredibly fortunate to have had the opportunity to collaborate with exceptional individuals throughout my research journey. Debabrota Basu, Dmitry Malioutov, Krisnha P. Gummadi, Daniel Neider, Arijit Khan, Jonathan Scarlet, Chandrika Bhardwaj, Vijay Saraswat, Naheed Anjum Arafat, and Lorenzo Ciampiconi are among the remarkable collaborators who have generously shared their knowledge and experience with me. I come to understand that finding a meaningful research problem is a crucial step and I am grateful to have had the opportunity to collaborate and brainstorm with such insightful collaborators. In addition, I thank Harold Soh and Reza Shokri, who examine my thesis with utmost attention. Their feedback has been a driving force for me to reflect positively on my thesis, building a mindset for a broader view on research in general.

I would like to express my sincere appreciation to my friends in Singapore who have provided invaluable support throughout my journey. Neamul Kabir, Sanjay Saha, Amlan Saha, Rafiul Islam, Zubair Faruqui, Mohimenul Mahi, Ramzan Miah, Muhim Muktadir Zim, and Shayok Ghosh have been pillars of support and encouragement. I am also grateful for the exceptional colleagues who have made a significant impact on my professional growth. Priyanka Golia, Teodora Baluta, Yash Pote, Arijit Shaw, Suwei Yang, Jiong Yang, Mate Soos, Tim van Bremen, Anna Latour, Yacine Izza, Gunjan Kumar, Paulius Dilkas, Shubham Sharma, Rahul Gupta, and Zhanzhong Pang have been sources of inspiration and collaboration. Additionally, I would like to extend a special thank you to my childhood friends, Kalyan Roy, Sukanto Kundu, Nayem Ul Haque, and Niranjan Chandra Roy.   I am fortunate to have such a supportive community. I extend my thanks to all the staff members in SOC, NUS for their exceptional efficiency in addressing out needs.

I would like to express my heartfelt gratitude to my family for their support and encouragement. My parents, sister, brother-in-law, and uncle have been constant pillars of strength throughout my journey. While I deeply regret that my father is not here with me today, I find solace in the belief that his blessings will always guide me. I am also immensely grateful to my wife, Dola Ghosh, who has been my unwavering source of support and companionship throughout this challenging journey. Her presence has made the road to completion much smoother, and I am grateful for her love and encouragement. 
%Their friendship has been a constant source of strength and support throughout my life.
